Robust Bayesian Analysis of Causal Inference Problems

### 2024-04-29 JASA-template.tex

Let $\pi_j$ denote the prior probability that the $j$-th
predictor is associated with the outcome or the 
treatment. That is, conceptually,
\begin{equation}
	\pi_j \coloneqq P\left((\beta_j,\gamma_j)\not=(0,0)\right).
\end{equation}
Practically, we model this by defining the following hierarchical model
so that,
for $1\le j\le p$,
\begin{align}
	(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
	\pi_{j}\normal\left( \begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_1^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)
	+ (1-\pi_{j}) \normal\left(\begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_0^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)\\
	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
        \frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
	\pi_{j} &\sim\text{Beta}\left(sq_j, s(1-q_j)\right).
\end{align}
In the hierarchical model, we fix sufficiently small $\tau_0$
$(1\gg\tau_0>0)$ so that  $(\beta_j, \gamma_j)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat beyond the spike component at the origin. 
We illustrate the components of a bivariate spike and slab prior in 
\cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
with $\tau_0=0.001$ and the slab component with $\tau_1=5$.

@@

Moreover, with our variable selection we only determine whether the variable 
is included in at least one of the models.
%%% MT to BT: I edited this paragraph for clarity; check
%But, we cannot determine a specific 
%association. Therefore, to adjust the sparsity of the estimates and understand
%the specific association with the treatment/outcome/both, 
To determine which predictors
influence the outcome ($\beta_j\neq 0$),
the treatment ($\gamma_j\neq 0$), or both,
and to understand the degree of assocation
(i.e.\ the magnitude of $\beta_j$ and/or $\gamma_j$),
we apply the 
``decoupled shrinkage and selection'' (DSS) method proposed by \citep{hahn2015}. 
For that, we solve the following adaptive LASSO-type \citep{Zou2006}
problems:
\begin{align}
	\hat{\beta}^D_{S(q)} &= 
	\arg\min_{\beta_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\beta}_{S(q)}
	- X_{S(q)} \beta_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
	\frac{|\beta_{j,S(q)}|}{|\hat{\beta}_{j,S(q)}|}
\end{align}
and
\begin{align}
	\hat{\gamma}^D_{S(q)} &= 
	\arg\min_{\gamma_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\gamma}_{S(q)}
	- X_{S(q)} \gamma_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
	\frac{|\gamma_{j,S(q)}|}{|\hat{\gamma}_{j,S(q)}|}
\end{align}
where $q\in \mathcal{P}$,
where $\hat{\beta}_{S(q)}$ 
and $\hat{\gamma}_{S(q)}$ are the posterior means 
of the regression coefficients with respect to
the predictors that belong to $S(q)$.
By varying $q$, this gives us a set of point estimates for the model parameters $\beta$ and $\gamma$.

@@

To do so, we can again use our Bayesian model without $\pi_j$ (i.e. there is no selection), and with
\begin{align}
\beta_j\sim\mathcal{N}(0,\tau_1\sigma^2)
\end{align}

@@

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Tue May 23 18:29:20 2023
% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Mar 25 09:52:08 2024
\begin{table}[ht]
\centering
\tiny
\caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
\begin{tabular}{c|ccccc|ccccc}
  \hline
 Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
  \hline
 & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
  \hline
25 & 3.06 & 4.18 & -- & -- & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
  30 & 3.47 & 4.31 & -- & -- & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
  35 & 3.24 & 3.53 & -- & -- & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
  40 & 3.61 & 3.83 & -- & -- & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
  45 & 3.80 & 3.87 & -- & -- & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
  50 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
  55 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
  60 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
  65 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
  70 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
  75 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
  80 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
  85 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
  90 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
  95 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
  100 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
  105 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
  110 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
  115 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
  120 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  125 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  130 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
  135 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
  140 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  145 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  150 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
  155 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
  160 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  165 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
  170 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
  175 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
  180 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  185 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  190 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  195 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  200 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
   \hline
\end{tabular}
\label{tab:causal1}
\end{table}
\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
    \label{fig:comp:trt}
\end{figure}

@@

 Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 

@@

25 &   0 &   0 &  43 & 8.6 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0&   0  \\ 
  30 &   0 &   0 &   5 & 1 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
  35 &   0 &   0 &   2 & .4 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
  40 &   0 &   0 &   0 & 0 &  -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
  45 &   0 &   0 &   0 & 0 & -- &  --  &  -- &  --  &  -- &  --  &    0 &   0 &   0 \\ 

@@

  110 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0&   0 &   0 &   0  &   0 \\ 

@@

  155 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &  0 &   0 &   0 &   0 &   0 &   0 \\ 
  160 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  165 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  170 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  175 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  180 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  185 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  190 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  195 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  200 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 

@@

25 &   0 &   1 &  21 & 5.2 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
  30 &   0 &   0 &  44 & 8.8 & -- &  --  &  -- &  --  &  -- &  --  &  0 &  13 &   13\\ 
  35 &   0 &   0 &  11 & 2.2 & -- &  --  &  -- &  --  &  -- &  --  &  0 &  13 &   13\\ 
  40 &   0 &   0 &   4 & .8 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
  45 &   0 &   0 &   3 & .6 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
  50 &   0 &   0 &   2 & .1 &  0 &   0 &   0 &   0 &  15 & 15 &   0 &   0 &   0\\ 
  55 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  60 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  65 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  70 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  75 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  80 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  85 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  90 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  95 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  100 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  105 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  110 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  115 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  120 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  125 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  130 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  135 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  140 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  145 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  150 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  155 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  160 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  165 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  170 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  175 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  180 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  185 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  190 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  195 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
  200 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 

>>>>

Let $\pi_j$ denote the prior probability that the $j$-th
predictor is associated with the outcome or the 
treatment. That is, conceptually,
\begin{equation}
	\pi_j \coloneqq P\left((\beta_j,\gamma_j)\not=(0,0)\right).
\end{equation}
Practically, we model this by defining the following hierarchical model
so that,
for $1\le j\le p$,
\begin{align}
	\label{eq:spike:slab:prior:beta:gamma}(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
	\pi_{j}\normal\left( \begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_1^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)
	+ (1-\pi_{j}) \normal\left(\begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_0^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)\\
	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
        \frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
	\pi_{j} &\sim\text{Beta}\left(sq_j, s(1-q_j)\right).
\end{align}
In the hierarchical model, we fix sufficiently small $\tau_0$
$(1\gg\tau_0>0)$ so that  $(\beta_j, \gamma_j)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat beyond the spike component at the origin. 
We illustrate the components of a bivariate spike and slab prior in 
\cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
with $\tau_0=0.001$ and the slab component with $\tau_1=5$.

@@

Moreover, with our variable selection we only determine whether the variable 
is included in at least one of the models.
%%% MT to BT: I edited this paragraph for clarity; check
%But, we cannot determine a specific 
%association. Therefore, to adjust the sparsity of the estimates and understand
%the specific association with the treatment/outcome/both, 
To determine which predictors
influence the outcome ($\beta_j\neq 0$),
the treatment ($\gamma_j\neq 0$), or both,
and to understand the degree of assocation
(i.e.\ the magnitude of $\beta_j$ and/or $\gamma_j$),
we apply the 
``decoupled shrinkage and selection'' (DSS) method proposed by \citep{hahn2015}. 
For that, we solve the following adaptive LASSO-type \citep{Zou2006}
problems:
\begin{align}
	\hat{\beta}^D_{S(q)} &= 
	\arg\min_{\beta_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\beta}_{S(q)}
	- X_{S(q)} \beta_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
	\frac{|\beta_{j,S(q)}|}{|\hat{\beta}_{j,S(q)}|}
\end{align}
and
\begin{align}
	\hat{\gamma}^D_{S(q)} &= 
	\arg\min_{\gamma_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\gamma}_{S(q)}
	- X_{S(q)} \gamma_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
	\frac{|\gamma_{j,S(q)}|}{|\hat{\gamma}_{j,S(q)}|}
\end{align}
where $q\in \mathcal{P}$,
where $\hat{\beta}_{S(q)}$ 
and $\hat{\gamma}_{S(q)}$ are the posterior means 
of the regression coefficients with respect to
the predictors that belong to $S(q)$.
By varying $q$, this gives us a set of point estimates for the model parameters $\beta$ and $\gamma$, along with a more detailed selection of individual $\beta_j$ and $\gamma_j$.

@@

To do so, we can again use our Bayesian model without $\pi_j$ (as there is no selection anymore), and with priors
\begin{align}
\beta_j\mid\sigma^2&\sim\mathcal{N}(0,\tau_1^2\sigma^2) \\
\gamma_j\mid\sigma^2&\sim\mathcal{N}(0,\tau_1^2)
\end{align}
for those $\beta_j$ and $\gamma_j$ that are selected in the model, with the remaining $\beta_j$ and $\gamma_j$ set to zero.
This is similar to the spike and slab prior from \cref{eq:spike:slab:prior:beta:gamma} but without the spike component.

We expect this to have only a small effect on the mean and variance of the estimated parameters. This refit is useful to validate the variable selection and to improve the estimating of the model parameters, including the causal effect $\beta_T$. Indeed, since there are fewer parameters for the same data, the estimates are expected to have less uncertainty.

Note that here, we described a precise Bayesian refit model, but obviously this could be extended to robust Bayesian refit models too.

@@

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Tue May 23 18:29:20 2023
% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Mar 25 09:52:08 2024
\begin{table}[ht]
\centering
\tiny
\caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
\begin{tabular}{c|ccccc|ccccc}
  \hline
 Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
  \hline
 & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
  \hline
25 & 2.61 & 3.38 &  &  & 2.19 & 2.70 & 3.29 &  &  & 8.80 \\ 
  30 & 3.14 & 3.56 &  &  & 3.99 & 3.01 & 3.54 &  &  & 9.02 \\ 
  35 & 3.15 & 3.52 &  &  & 3.98 & 3.22 & 3.66 &  &  & 6.66 \\ 
  40 & 3.60 & 3.75 &  &  & 3.98 & 3.20 & 3.70 &  &  & 4.42 \\ 
  45 & 3.76 & 3.82 &  &  & 3.96 & 3.61 & 3.74 &  &  & 3.99 \\ 
  50 & 3.79 & 3.84 & 3.99 & 4.01 & 3.99 & 3.75 & 3.79 & 9.04 & 9.36 & 4.01  \\ 
  55 & 3.89 & 3.91 & 3.97 & 4.00 & 3.98 & 3.77 & 3.81 & 5.92 & 6.38 & 4.02 \\ 
  60 & 3.93 & 3.95 & 3.99 & 4.00 & 3.98 & 3.76 & 3.77 & 3.89 & 3.50 & 4.03 \\ 
  65 & 3.95 & 3.96 & 4.00 & 4.02 & 4.00 & 3.76 & 3.78 & 3.91 & 3.99 & 4.02 \\ 
  70 & 3.94 & 3.96 & 4.01 & 4.05 & 4.00 & 3.77 & 3.79 & 4.01 & 3.96 & 4.03 \\ 
  75 & 3.97 & 3.98 & 4.02 & 4.03 & 4.02  & 3.82 & 3.83 & 4.03 & 4.02 & 4.04 \\ 
  80 & 3.96 & 3.98 & 4.02 & 4.05 & 4.01 & 3.83 & 3.85 & 4.04 & 4.05 & 4.05 \\ 
  85 & 3.96 & 3.98 & 4.03 & 4.04 & 4.03 & 3.84 & 3.86 & 4.05 & 4.06 & 4.06 \\ 
  90 & 3.97 & 3.99 & 4.05 & 4.07 & 4.04 & 3.87 & 3.88 & 4.06 & 4.04 & 4.05 \\ 
  95 & 3.96 & 3.98 & 4.02 & 4.05 & 4.04 & 3.88 & 3.89 & 4.05 & 4.06 & 4.06 \\ 
  100 & 3.95 & 3.98 & 4.03 & 4.05 & 4.04 & 3.88 & 3.89 & 4.07 & 4.06 & 4.07 \\ 
  105 & 3.97 & 3.98 & 4.03 & 4.05 & 4.03 & 3.89 & 3.90 & 4.07 & 4.06 & 4.07 \\ 
  110 & 3.97 & 3.99 & 4.03 & 4.05 & 4.03 & 3.90 & 3.91 & 4.07 & 4.05 & 4.07 \\ 
  115 & 3.98 & 3.99 & 4.04 & 4.05 & 4.04 & 3.91 & 3.92 & 4.06 & 4.06 & 4.06 \\ 
  120 & 3.98 & 3.99 & 4.04 & 4.05 & 4.03 & 3.91 & 3.92 & 4.04 & 4.05 & 4.04 \\ 
  125 & 3.99 & 3.99 & 4.03 & 4.04 & 4.03 & 3.91 & 3.92 & 4.04 & 4.04 & 4.04 \\ 
  130 & 3.98 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.93 & 4.03 & 4.04 & 4.04 \\ 
  135 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.94 & 3.94 & 4.04 & 4.05 & 4.04 \\ 
  140 &  3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 4.04 & 4.05 & 4.04 \\ 
  145 & 3.99 & 3.99 & 4.03 & 4.04 & 4.03 & 3.95 & 3.95 & 4.05 & 4.05 & 4.05 \\ 
  150 & 3.99 & 3.99 & 4.02 & 4.02 & 4.02 & 3.94 & 3.95 & 4.04 & 4.04 & 4.04 \\ 
   \hline
\end{tabular}
\label{tab:causal1}
\end{table}
\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
    \label{fig:comp:trt}
\end{figure}

@@

 Obs & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 

@@

25 & 1 & 0 & 39 & 8.8 &  &  &  &  &  &  & 9 & 1 & 10 \\ 
  30 & 0 & 0 & 3 & 0.6 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
  35 & 0 & 0 & 3 & 0.6 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
  40 & 0 & 0 & 0 & 0 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
  45 & 0 & 0 & 0 & 0 &  &  &  &  &  &  & 0 & 0 & 0 \\ 

@@

  110 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 

@@

@@

25 &   5 & 0 & 35 & 12 &  &  &  &  &  &  & 0 & 15 & 15 \\ 
  30 & 0 & 2 & 7 & 3.4 &  &  &  &  &  &  & 0 & 14 & 14 \\ 
  35 & 0 & 1 & 9 & 2.8 &  &  &  &  &  &  & 0 & 14 & 14 \\ 
  40 & 0 & 0 & 21 & 4.2 &  &  &  &  &  &  & 0 & 10 & 10 \\ 
  45 & 0 & 0 & 1 & 0.2 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
  50 & 0 & 0 & 0 & 0 & 0 & 15 & 15 & 0 & 15 & 15 & 0 & 0 & 0 \\ 
  55 & 0 & 0 & 0 & 0 & 0 & 14 & 14 & 0 & 14 & 14 & 0 & 0 & 0 \\ 
  95 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  100 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  110 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  145 & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
